MIGRACE DAT - DEMUS / MUSEION

### 2023-02-13 MSK_MUZBE_bioslovniky.Rmd
all added to main branch to prevent overwrite

---
title: "MIGRACE DAT - DEMUS / MUSEION"
subtitle: "Prirodovedne sbirky - BIO slovniky"
author: "Katerina Krizova"
date: "2023-02-08"
output:
  pdf_document
    toc: true
    toc_depth: 2
    number_sections: false
    fig_caption: true
  fontsize: 11pt
  geometry: margin=1in

@@

>>>>

---
title: "MIGRACE DAT - DEMUS / MUSEION"
subtitle: "Moravskoslezsky kraj - Muzeum Beskyd"
author: "Katerina Krizova"
date: "2023-02-08"
output:
  pdf_document
    toc: true
    toc_depth: 2
    number_sections: false
    fig_caption: true
  fontsize: 11pt
  geometry: margin=1in

@@

```{r READ AND MODIFY DB TABLE PLANT, warning = F}

db_tab <- RODBC::sqlFetch(con, "botanika aktuální")            # read specific table

plant <- db_tab %>% 
  select(celed, druh, syn, var) %>% 
   separate(celed,into=c("celed_LAT", "celed_CZ") , sep=" ") %>% 
   separate(druh,into=c("rod_LAT", "druh_LAT", "autor") , sep=" ") %>% 
   mutate(celed_CZ = gsub("[()]", "", celed_CZ))

colnames(plant)
